---
title: "p8105_hw6_cm4070"
author: "Claire Mobley"
date: "12/1/2021"
output: github_document 
---

```{r}
library(tidyverse)
set.seed(1)
library(rvest)
library(modelr)
library(mgcv)
library(patchwork)

knitr::opts_chunk$set(
  fig.width = 6,
  fig.asp = .6,
  out.width = "90%"
)
theme_set(theme_minimal() + theme(legend.position = "bottom"))
options(
  ggplot2.continuous.colour = "viridis",
  ggplot2.continuous.fill = "viridis"
)
scale_colour_discrete = scale_colour_viridis_d
scale_fill_discrete = scale_fill_viridis_d
```

## Problem 1

## Load and Clean the `Birthweight` Dataset

This code will change the babysex numeric variable into a factor with 2 levels, "male" and "female", the frace numeric variable into factor variable with levels,  "white", "black", "asian", "puerto rican", "other", "unknown", and the m race variable into factor variable with levels "white", "black", "asian", "puerto rican", "other", and look for any missing values.

```{r}
birthweight_data = read_csv("./birthweight.csv") %>% 
 mutate(babysex = factor(babysex, levels = c("1", "2"), labels = c("male", "female")),
        frace = factor(frace, levels = c("1", "2", "3", "4", "8", "9"), labels = c("white", "black", "asian", "puerto rican", "other", "unknown")), 
        malform = factor(malform, levels = c("0", "1"), labels = c("absent", "present")),
        mrace = factor(mrace, levels = c("1", "2", "3", "4", "8"), labels = c("white", "black", "asian", "puerto rican", "other"))) 

sum(is.na(birthweight_data))
```

## Propose a regression model 

The code below will propose a model for birthweight. Based on scientific literature regarding predictors of child birthweight, I propose the following variables are contributors to overall birthweight and important to be included in the model.

```{r}
fit = lm(bwt ~ babysex + delwt + gaweeks + mheight + momage + smoken, data = birthweight_data)

broom::tidy(fit)
broom::glance(fit)
```

## Diagnostics

This code will provide a plot of model residuals against fitted values.

```{r}
birthweight_data %>% 
  modelr::add_residuals(fit) %>% 
  modelr::add_predictions(fit) %>% 
  ggplot(aes(x = pred, y = resid)) +
  geom_point()
```

## Compare to other models

This model uses length at birth and gestational age as predictors

```{r}
fit1 = lm(bwt ~ blength + gaweeks, data = birthweight_data)

broom::tidy(fit1)
```

This model uses head circumference, length, sex, and all interactions between these as predictors

```{r}
fit2 = lm(bwt ~ bhead * blength * babysex, data = birthweight_data)

broom::tidy(fit2)
```

## Cross validation

This code will make a comparison between the models in terms of the cross-validated prediction error.

```{r}
cv_df =
  crossv_mc(birthweight_data, 100) %>% 
  mutate(
    train = map(train, as_tibble),
    test = map(test, as_tibble))
```

```{r}
cv_df = 
  cv_df %>% 
  mutate(
    mine_mod  = map(train, ~lm(bwt ~ babysex + delwt + gaweeks + mheight + momage + smoken, data = .x)),
     maineffect_mod = map(train, ~lm(bwt ~ blength + gaweeks, data = .x)),
    interaction_mod = map(train, ~lm(bwt ~ bhead * blength * babysex, data = as_tibble(.x)))) %>% 
  mutate(
    rmse_mine = map2_dbl(mine_mod, test, ~rmse(model = .x, data = .y)),
    rmse_maineffect = map2_dbl(maineffect_mod, test, ~rmse(model = .x, data = .y)),
    rmse_interaction = map2_dbl(interaction_mod, test, ~rmse(model = .x, data = .y)))
```

```{r}
cv_df %>% 
  select(starts_with("rmse")) %>% 
  pivot_longer(
    everything(),
    names_to = "model", 
    values_to = "rmse",
    names_prefix = "rmse_") %>% 
  mutate(model = fct_inorder(model)) %>% 
  ggplot(aes(x = model, y = rmse)) + geom_violin()
```

